On Extending a Full-Sharing Design with Batched Scheduling

### 2015-04-16 paper.tex
removing stuff

By observing Table~\ref{tab_batched_overhead}, we can see that, for 1
thread, on the average overhead ratio, local scheduling is sightly
better than batched on the two designs. For the NS design we have
$0.78$ and $0.82$ and for the FS design we have $1.30$ and $1.46$
average overhead ratios, for the local and batched scheduling
strategies, respectively.

>>>>

By observing Table~\ref{tab_batched_overhead}, we can see that, for 1
thread, on the minimum overhead ratio, local scheduling is better on
the NS design, while batched scheduling is better in the FS
design. For the average and maximum overhead ratios, in the FS design,
the best strategy is always the local scheduling.
